Bioverse: Origins of Life

### 2023-08-25 src/tex/ms.tex
add schematic figure with OOL scenarios
structure paper outline

\section{Introduction}
\label{sec:intro}

\section{Origins of Life Scenarios and their predictions}
\label{sec:ool_scenarios}
In this section, we present some of the most prominent origins of life scenarios and their observational predictions.
We focus on the necessary environmental conditions for the processes and reactions inherent to each scenario, and aim to identify distinct observables that are accessible via present and near-future remote sensing techniques.

@@

\include{bayesian_analysis}

@@

\subsection{Habitable Worlds Observatory}
\subsubsection{target list}
Provisional stellar target List for the habitable Worlds Observatory~\citep{Mamajek2023}.

@@

\section{Hypothesis tests}
\label{sec:hypotests}
\subsection{Possibility of hydrothermal vents}

\subsection{Availability of rock-air interfaces}

\subsection{Planetary redox state evolution}

\subsection{Planetary UV flux and its evolution}

\section{Results}
\label{sec:results}

@@

''Which natural processes best explain how living matter spontaneously appears from nonliving matter?''~\citep{Malaterre2022}
%WE consider life ``as we know it''

>>>>

\section{Introduction}
\label{sec:intro}
\todo[inline]{Introduce OOL, the importance of planetary contexts}

\section{Origins of Life Scenarios and their predictions}
\todo[inline]{Present widely discussed OOL scenarios and their predictions on exoplanet observables; derive testable hypotheses.}
\label{sec:ool_scenarios}
In this section, we present some of the most prominent origins of life scenarios and their observational predictions.
We focus on the necessary environmental conditions for the processes and reactions inherent to each scenario, and aim to identify distinct observables that are accessible via present and near-future remote sensing techniques.

@@

%\include{bayesian_analysis}

\subsubsection{Origins of Life Hypotheses}
...
\begin{figure*}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/hypotheses.pdf}
        \caption{Origins of Life scenarios, their predictions on exoplanet observables, and derived population-level hypotheses.}
        \label{fig:hypotheses}
    \end{centering}
\end{figure*}
Figure~\ref{fig:hypotheses} lists the hypotheses derived from the predictions of each OOL scenario.
...

@@

\subsection{Habitable Worlds Observatory}
\subsubsection{target list}
\todo[inline]{Provisional stellar target List for the habitable Worlds Observatory:~\citep{Mamajek2023}}

@@

\section{Hypothesis tests}
\label{sec:hypotests}
\todo[inline]{Briefly introduce Bayesian model comparison, then present the particular hypotheses in their mathematical form.}
\subsection{H1: Life only originates in hydrothermal vents}

\subsection{H2: Life only originates in subaerial ponds with wet/dry cycles}

\subsection{H3: Life only originates on planets with particular UV irradiance}

\section{Results}
\label{sec:results}
\subsection{Information content in mass-density space}

\subsection{Information content in tidal locking timescale-density space}

\subsection{Correlation of past UV flux and biosignature occurrence}

@@

%''Which natural processes best explain how living matter spontaneously appears from nonliving matter?''~\citep{Malaterre2022}
%WE consider life ``as we know it''
